Turbulence in compact to giant H~II regions

### 2023-04-24 strucfunc_paper.tex
Finish the revision of Hubble V and X sections

\usepackage{upgreek}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

@@

\appendix
\colorlet{RED}{red}
\startNEW
\section{Degradation of the structure function due to observational limitations}
\label{sec:degr-struct-funct}
\stopNEW
% Studied in context of \(\Delta\)-variance by \citet{Bensch:2001l}.

@@

We find that the following simple analytic function reproduces
these results to within better than 10\%:
%\begin{equation}\label{eq:seeingemp2}
%S(r; s_0, r_0) = \frac{e^{-s_0 / r_0}}{1+(2s_0 / r)^{2a}} ,
%\end{equation}
\begin{equation}\label{eq:seeingemp2}
  \startNEW
  S(r; s_0, r_0) = 
  \left [
    \left (1+a_1\frac{s_0}{r_0} \right) 
    \left(1+ \left (a_2 \frac{ s_0}{r} \right) ^{a_3} \right)
  \right ]^{-1} ,
  \stopNEW
\end{equation}
which is shown by dashed lines in \NEW{Figure \ref{fig:seeing-reduction}b}.
\NEW{%
  The exact values of the constants \(a_1\), \(a_2\), \(a_3\)
  are found to depend slightly on the power law slope \(m\)
  and the magnitude of the emissivity fluctuations \(\shortsig{E}\).
  We adopt the compromise values \(a_1 = 1.25\),
  \(a_2 = 2.6\), and \(a_3 = 1.5\), which fit the numerical results to
  within 20\% for \(0.8 < m < 1.2\) and \(0.5 < \shortsig{E} < 2.0\).}
The optimum value of the index \(a\) in this equation varies slightly
with the power law slope \(m\) of the true structure function,
but a compromise value of \(a = 0.75\) works tolerably well for \(m = 0.7\) to \(1.3\).
We therefore use this equation to represent the seeing
in our structure function fits (section~\ref{sec:results}),
with \(s_0\) as an additional free parameter for the models.
\clearpage

@@

\subsection{Hubble X and Hubble V in NGC 6822}
\label{sec:6822-hubble}
%
The irregular dwarf galaxy, NGC 6822, is located at a distance of 500 kpc \citetext{\SI{1}{\arcsecond} = \SI{2.42}{pc} ; \citealp{2012A&A...540A.135S}} and host the \hii{} regions Hubble X and Hubble V which are the brightest regions in the galaxy.

Hubble V is located near the 'Hodge OB 8' OB association with a number of \num{\sim 36} young stellar objects \citep{2021MNRAS.507.5106K} and its core is powered by an O3 V star \citep{1999PASP..111.1382O}.
It has an ionizing output \(Q_0\) of \SI{e50.23}{photons.s^{-1}} (13 times higher compared to the Orion Nebula) and has a \ha{} luminosity of \SI{e38.30}{erg.s^{-1}}\citep{2002MNRAS.329..481B}.
The mean non-thermal linewidth in \ha{} \SI{10.3 \pm 0.03}{km.s^{-1}} \citep{1986A&A...160..374H}.

Hubble X is located near the 'Hodge OB 13' OB association with a number of \num{\sim 29} young stellar objects \citep{2021MNRAS.507.5106K} and its core is powered by and O4 V star \citep{1999PASP..111.1382O}.
It has an ionizing output \(Q_0\) of \SI{e50.14}{photons.s^{-1}} (10 times higher compared to the Orion Nebula) and has a \ha{} luminosity of \SI{e38.21}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
The mean non-thermal linewidth in \ha{} is \SI{10.5 \pm 0.02}{km.s^{-1}}  \citep{1986A&A...160..374H}.
\citet{1993PASJ...45..693T} realize a study on the kinematics of both regions.

@@

In the Figure~\ref{fig:strucfunc-fit-ExtraGal}a we show the structure function of Hubble V.
The value of the observed \(\sigma\pos^2 = \SI{8}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{3}{pc} \) (while the derived values from our model are \(\sigma\pos^2 = \SI{10}{km^{2}.s^{-2}}\) and \(r_0 = \SI{3.6}{pc} \)).
The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{31}{pc} \).
The maximum \(B(r)\) value is \SI{18}{km^{2}.s^{-2}} at a separation of \SI{25}{pc}. 
%The value of the seeing for this regions is \SI{0.5}{pc} (\(s_0\)=\SI{0.2}{\arcsecond}).
From this value the \(B(r)\) values decrease and we observe a downturn in the structure function to \SI{9}{km^{2}.s^{-2}} at \(r =  \SI{70}{pc}\) following the tapered fluctuations behavior.
But unlike the Orion core or 30~Dor the downturn is not as smooth, since it presents a small variation at \(r = \SI{\sim 40}{pc} \) 
The seeing (RMS) value derived for this regions is \SI{0.5}{pc} (\(s_0\)=\SI{0.2}{\arcsecond}) and just one point of the structure function fall in the confidence interval..
Considering the first point above this \(s_0\) value to be valid, which corresponds to \SI{2.2}{km^{2}.s^{-2}} at \(r = \SI{0.89}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{1.06} and \num{0.55}, respectively, while our derived value is \num{0.81}.

The Hubble X structure function is shown in Figure~\ref{fig:strucfunc-fit-ExtraGal}b.
The value of the observed \(\sigma\pos^2 = \SI{13}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{4}{pc} \) (while the derived values from our model are \(\sigma\pos^2 = \SI{15}{km^{2}.s^{-2}}\) and \(r_0 = \SI{4}{pc} \)).
The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{15}{pc} \).
The maximum \(B(r)\) value of \SI{31}{km^{2}.s^{-2}} is reached at a separation of \SI{36}{pc}.
From scales \(> \SI{15}{pc}\) we see that the structure functions fluctuates around \(2\sigma\pos^2\) with a spatial wavelength of \(\sim \SI{30}{pc}\) with a dispersion of \SI{2.3}{km^{2}.s^{-2}}.
Since these large scales values fluctuates around \(2\sigma\pos^2\) is also possible that the structure function follows a purely homogeneous fluctuations behavior, just not as marked as it is shown in section~\ref{sec:limit-model-struct}. 
The seeing is \SI{0.6}{pc} (\(s_0\)=\SI{0.24}{\arcsecond}) and as in Hubble V there is just one point of the structure function that falls in the \(s_0\) confidence interval.
Considering the first point above this \(s_0\) value to be valid, which corresponds to \SI{2.6}{km^{2}.s^{-2}} at \(r = \SI{0.86}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{1.04} and \num{0.80}, respectively, while our derived value is \num{1.02}.

>>>>

\usepackage{upgreek}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{placeins}
%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

@@

\appendix

% Be more lenient about float placement
\renewcommand\textfraction{0.0}
\renewcommand\topfraction{1.0}
\renewcommand\bottomfraction{1.0}

\startNEW
\section{Degradation of the structure function due to observational limitations}
\label{sec:degr-struct-funct}
\stopNEW
% Studied in context of \(\Delta\)-variance by \citet{Bensch:2001l}.

@@

We find that the following simple analytic function reproduces
these results to within better than 10\%:
%\begin{equation}\label{eq:seeingemp2}
%S(r; s_0, r_0) = \frac{e^{-s_0 / r_0}}{1+(2s_0 / r)^{2a}} ,
%\end{equation}
\begin{equation}\label{eq:seeingemp2}
  \startNEW
  S(r; s_0, r_0) = 
  \left [
    \left (1+a_1\frac{s_0}{r_0} \right) 
    \left(1+ \left (a_2 \frac{ s_0}{r} \right) ^{a_3} \right)
  \right ]^{-1} ,
  \stopNEW
\end{equation}
which is shown by dashed lines in \NEW{Figure \ref{fig:seeing-reduction}b}.
\NEW{%
  The exact values of the constants \(a_1\), \(a_2\), \(a_3\)
  are found to depend slightly on the power law slope \(m\)
  and the magnitude of the emissivity fluctuations \(\shortsig{E}\).
  We adopt the compromise values \(a_1 = 1.25\),
  \(a_2 = 2.6\), and \(a_3 = 1.5\), which fit the numerical results to
  within 20\% for \(0.8 < m < 1.2\) and \(0.5 < \shortsig{E} < 2.0\).}
The optimum value of the index \(a\) in this equation varies slightly
with the power law slope \(m\) of the true structure function,
but a compromise value of \(a = 0.75\) works tolerably well for \(m = 0.7\) to \(1.3\).
We therefore use this equation to represent the seeing
in our structure function fits (section~\ref{sec:results}),
with \(s_0\) as an additional free parameter for the models.

\FloatBarrier

@@

\subsection{Hubble X and Hubble V in NGC 6822}
\label{sec:6822-hubble}
%
The irregular dwarf galaxy, NGC 6822, is located at a distance of \SI{500}{kpc} \citetext{\SI{1}{\arcsecond} = \SI{2.42}{pc}; \citealp{2012A&A...540A.135S}} and hosts the \hii{} regions Hubble~X and Hubble~V which are the brightest regions in the galaxy
\NEW{\citep{Hodge:1989c}}.

Hubble V is located near the ``Hodge OB 8'' OB association with a number of \num{\sim 36} young stellar objects \citep{2021MNRAS.507.5106K} and its core is powered by an O3 V star \citep{1999PASP..111.1382O}.
It has an ionizing output \(Q_0\) of \SI{e50.23}{photons.s^{-1}} (13 times higher compared to the Orion Nebula) and has a \ha{} luminosity of \SI{e38.30}{erg.s^{-1}}\citep{2002MNRAS.329..481B}.
The mean non-thermal linewidth in \ha{} \(\sigma\los = \SI{10.3 \pm 0.03}{km.s^{-1}}\) \citep{1986A&A...160..374H}.

Hubble X is located near the Hodge ``OB 13'' OB association with a number of \num{\sim 29} young stellar objects \citep{2021MNRAS.507.5106K} and its core is powered by an O4 V star \citep{1999PASP..111.1382O}.
It has an ionizing output \(Q_0\) of \SI{e50.14}{photons.s^{-1}} (10 times higher compared to the Orion Nebula) and has a \ha{} luminosity of \SI{e38.21}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
The mean non-thermal linewidth in \ha{} is \(\sigma\los = \SI{10.5 \pm 0.02}{km.s^{-1}}\)  \citep{1986A&A...160..374H}.
\citet{1993PASJ...45..693T} studies the kinematics of both regions.

@@

In the Figure~\ref{fig:strucfunc-fit-ExtraGal}a we show the structure function of Hubble V.
\startNEW
The model-derived parameters are \(\sigma\pos^2 = \SI{10 \pm 3}{km^{2}.s^{-2}}\),
\(r_0 = \SI{3.6 \pm 1.0}{pc} \)), and \(m = 0.8 \pm 0.3\).
The velocity variance is slightly higher than the empirically derived value of \(\sigma\pos^2 = \SI{8}{km^{2}.s^{-2}}\) because the model-derived seeing is only 6 times smaller than the correlation length.

At the largest scales, the structure function turns downward,
as seen in Orion.
However, inspection of the velocity map suggests that the explanation
may be different in this source: the velocity varies more strongly across the short axis of the nebula than along its long axis.
There is also marginal evidence for weak periodic fluctuations
with wavelength \(\lambda \approx \SI{50}{pc}\).
\stopNEW

The Hubble X structure function is shown in Figure~\ref{fig:strucfunc-fit-ExtraGal}b.
\startNEW
The model-derived parameters are \(\sigma\pos^2 = \SI{15 \pm 3}{km^{2}.s^{-2}}\),
\(r_0 = \SI{4.0 \pm 0.5}{pc} \)), and \(m = 1.0 \pm 0.2\),
which again is slightly higher than the empirically derived value of \(\sigma\pos^2 = \SI{13}{km^{2}.s^{-2}}\) because the latter is reduced by the seeing.

At the largest scales the structure function is approximately flat,
consistent with homogeneous fluctuations. 
\stopNEW
